European or American? A re-examination of the transatlantic influence over the IMF

### 2025-09-11 manuscript/manuscript.qmd
Major: fix 9th para to soften the tone

Several limitations of our analysis should be acknowledged. First, our sample period ends in 2010, just as the European sovereign debt crisis was beginning to reshape transatlantic dynamics within the IMF. The Fund's involvement in European bailouts through the Troika arrangements may have altered the balance of influence in ways not captured by our data. Future research should examine whether the patterns we document persist in the post-crisis period.

>>>>

Several limitations of our analysis should be acknowledged. First, our sample period ends in 2010, reflecting the coverage of the underlying datasets we rely on. While this prevents us from capturing the European sovereign debt crisis and the subsequent Troika arrangements, we expect that including the post-2010 period would, if anything, reinforce our findings. The IMF’s close collaboration with European institutions during the crisis suggests that European influence over lending decisions likely became even more pronounced after our period of observation.
